### 2020-07-20 code/figure1.Rmd
Update Figure 1F data with new umap_3d_coors object

####################
## Figure 1F data ##
####################
## reclassifying clust 0 using our classified cluster as training test and unclassified as test set
umap_2d_3d_coors$knn_clust <- umap_2d_3d_coors$clust
umap_2d_3d_coors$knn_clust[umap_2d_3d_coors$clust==0]<-class::knn(train = umap_2d_3d_coors[,c("x_3d", "y_3d", "z_3d")][which(umap_2d_3d_coors$clust!=0),],
                                                                  test = umap_2d_3d_coors[,c("x_3d", "y_3d", "z_3d")][which(umap_2d_3d_coors$clust==0),],
                                                                  cl = umap_2d_3d_coors$clust[umap_2d_3d_coors$clust!=0], 
                                                                  k=15)

>>>>

####################
## Figure 1F data ##
####################
## reclassifying clust 0 using our classified cluster as training test and unclassified as test set
umap_3d_coors$clust_knn <- umap_3d_coors$clust
umap_3d_coors$clust_knn[umap_3d_coors$clust == 0] <- class::knn(
  train = umap_3d_coors[which(umap_3d_coors$clust != 0), c("cluster_x", "cluster_y", "cluster_z")],
  test = umap_3d_coors[which(umap_3d_coors$clust == 0), c("cluster_x", "cluster_y", "cluster_z")],
  cl = umap_3d_coors$clust[umap_3d_coors$clust != 0], k = 87
)
